\abstractintoc
\thispagestyle{plain}
\renewcommand{\abstractname}{Abstract}
\renewcommand{\abstractnamefont}{\Large\textbf}
\renewcommand{\abstracttextfont}{\normalsize}

\begin{abstract}
\OnehalfSpacing

 For six months from September 2021 till February 2022, I did an internship at Node Robotics GmbH, a start-up company which offers a Autonomous intralogistics for the industries which enables the autonomous intralogistics. Node robotics core business involves offering plug&play software solutions for autonomous intralogistics. This internship is a part of my master program which I conduct at Darmstadt University of Applied Sciences, Darmstadt.
 
 During internship I worked as intern in Operations team. My main task during internship is to support for the backend. I worked on an project of developing a UI for rosbag analysis. In this my role is to develop and support in the ROS part of the project. This UI is used for the analysis of the rosbag and analyzing errors in the recorded bag provided by the customer. The main aim of the project is to visualize the map, laser scans, and position of the robot on the map. 
 
 My other work included in developing and including the new features for the existing backend for the frontend UI.
 
 Throughout the internship, I have also learnt many things about ROS, Docker etc. In short, I would like to thank Node robotics GmbH and Darmstadt University of Applied Sciences, Darmstadt, Internship Office for introducing me to this great opportunity in which I have developed myself both academically and professionally.
\end{abstract}
